Learning can mediate the evolution of (cheap and costly) signals of quality

### 2022-08-08 Presentations/ISBE2022.Rmd
FInal version of the ISBE2022 slides

```{r,echo=FALSE,fig.align='center',out.height='35%',fig.show='hold'}
knitr::include_graphics("../Images/Amotz_Zahavi_profile.jpg")
knitr::include_graphics("../Images/sexualSelection.jpg")
knitr::include_graphics("../Images/Grafen.jpg")
```

```{r,echo=FALSE,fig.align='center',out.height='35%'}

badQualRang<-seq(0,1,length=1000)
alpha<-0
beta<-6
costFunc<-function(beta,alpha,x) {d<-1/(1+exp(-alpha-beta*x))}
par(plt=posPlot())
betRang<-c(5)
matplot(y=sapply(betRang,FUN = costFunc,alpha=alpha,x=badQualRang),x=badQualRang,
        type="l",cex.lab=1.5, cex.axis=2,lwd=3,lty=1,las=1,
     col=c(2,3),ylim=c(0.5,1.1),xaxt="s",yaxt="s",ylab="",xlab="") #,col=i
# lines(badgeFunc(qualRange,3,-60,1.05)~qualRange,cex.lab=1.5,cex.axis=2,lwd=3,
#       col="blue")
# legend("bottomright",legend = betRang,title = expression(beta),col=1:3,
       # lty=1)
mtext(side=1,text="Quality",line=3.5,cex=3)
mtext(side=2,text="Survival",line=3.5,cex=3)

```
\vspace{-0.3cm}
[@zahavi_Mate_1975;@grafen_Biological_1990]

@@

```{r,echo=FALSE,fig.align='center',out.height='35%'}
knitr::include_graphics("../Images/learn_cartoon_2.png")
```

@@

```{r,echo=FALSE,fig.align='center',out.height='35%'}
knitr::include_graphics("../Images/learn_cartoon_5.png")
```

@@

<!-- \small -->
<!-- One of the replicates of the previous slide, the badge as a handicap -->
```{r, echo=FALSE,fig.align='center', out.width='90%'}
# knitr::include_graphics("../Simulations/betCostEvol1_/evolDyn0_betCost5.png")
knitr::include_graphics("../Simulations/betCostEvol2_/evolDyn18_betCost5.png")
```

@@

## Learning can mediate the evolution of Badges of Status
### Individual replicates: no badges
<!-- \small -->
<!-- One of the replicates where the badge did not evolve -->

```{r, echo=FALSE,fig.align='center', out.width='90%'}
knitr::include_graphics("../Simulations/betCostEvol2_/evolDyn19_betCost5.png")
```

@@

<!-- \small -->
<!-- Here simulations where the signal has no cost. -->

<!-- There seems to be some consistency in the three type of sender codes -->

```{r, echo=FALSE,fig.align='center', out.width='90%'}
knitr::include_graphics("../Simulations/nIntGroupNormQual_/evolDyn7_nIntGroup2000.png")
```

@@

```{r,echo=FALSE,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter0_.png")

@@

```{r,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter1_.png")

@@

```{r,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter2_.png")

>>>>

```{r,echo=FALSE,fig.align='center',out.height='45%',fig.show='hold'}
knitr::include_graphics("../Images/Amotz_Zahavi_profile.jpg")
knitr::include_graphics("../Images/sexualSelection.jpg")
knitr::include_graphics("../Images/Grafen.jpg")
```

<!-- # ```{r,echo=FALSE,fig.align='center',out.height='35%'} -->
<!-- #  -->
<!-- # badQualRang<-seq(0,1,length=1000) -->
<!-- # alpha<-0 -->
<!-- # beta<-6 -->
<!-- # costFunc<-function(beta,alpha,x) {d<-1/(1+exp(-alpha-beta*x))} -->
<!-- # par(plt=posPlot()) -->
<!-- # betRang<-c(5) -->
<!-- # matplot(y=sapply(betRang,FUN = costFunc,alpha=alpha,x=badQualRang),x=badQualRang, -->
<!-- #         type="l",cex.lab=1.5, cex.axis=2,lwd=3,lty=1,las=1, -->
<!-- #      col=c(2,3),ylim=c(0.5,1.1),xaxt="s",yaxt="s",ylab="",xlab="") #,col=i -->
<!-- # # lines(badgeFunc(qualRange,3,-60,1.05)~qualRange,cex.lab=1.5,cex.axis=2,lwd=3, -->
<!-- # #       col="blue") -->
<!-- # # legend("bottomright",legend = betRang,title = expression(beta),col=1:3, -->
<!-- #        # lty=1) -->
<!-- # mtext(side=1,text="Quality",line=3.5,cex=3) -->
<!-- # mtext(side=2,text="Survival",line=3.5,cex=3) -->
<!-- #  -->
<!-- # ``` -->

\vspace{0.6cm}
[@zahavi_Mate_1975;@grafen_Biological_1990]

@@

<!-- ## What about learning? -->

<!-- ```{r,echo=FALSE,fig.align='center',out.height='40%'} -->
<!-- knitr::include_graphics("../Images//pavlov.jpg") -->
<!-- ``` -->

<!-- ```{r,echo=FALSE,fig.align='center',out.height='35%'} -->
<!-- knitr::include_graphics("../Images/learn_cartoon_2.png") -->
<!-- ``` -->

@@

<!-- ## What about learning? -->

<!-- ```{r,echo=FALSE,fig.align='center',out.height='40%'} -->
<!-- knitr::include_graphics("../Images//pavlov.jpg") -->
<!-- ``` -->

<!-- ```{r,echo=FALSE,fig.align='center',out.height='35%'} -->
<!-- knitr::include_graphics("../Images/learn_cartoon_5.png") -->
<!-- ``` -->

@@

\column{0.05\linewidth}

\tiny
\vspace{1cm}

Receiver

\vspace{2cm}

Evolutionary  \\
Dynamics

\vspace{2cm}

Sender

\column{0.95\linewidth}

\includegraphics{../Simulations/betCostEvol2_/evolDyn18_betCost5_1.png}

\column{0.05\linewidth}

\tiny
\vspace{1cm}

Receiver

\vspace{2cm}

Evolutionary  \\
Dynamics

\vspace{2cm}

Sender

\column{0.95\linewidth}

\includegraphics{../Simulations/betCostEvol2_/evolDyn18_betCost5.png}

@@

<!-- ## Learning can mediate the evolution of Badges of Status -->
<!-- ### Individual replicates: no badges -->
<!-- <!-- \small --> 
<!-- <!-- One of the replicates where the badge did not evolve -->

<!-- \begin{columns}[T] -->

<!-- \column{0.05\linewidth} -->

<!-- \tiny -->
<!-- \vspace{1cm} -->

<!-- Receiver   -->

<!-- \vspace{2cm} -->

<!-- Evolutionary  \\ -->
<!-- Dynamics -->

<!-- \vspace{2cm} -->

<!-- Sender -->

<!-- \column{0.95\linewidth} -->

<!-- \includegraphics{../Simulations/betCostEvol2_/evolDyn19_betCost5.png} -->

<!-- \end{columns} -->

@@

\column{0.05\linewidth}

\tiny
\vspace{1cm}

Receiver

\vspace{2cm}

Evolutionary  \\
Dynamics

\vspace{2cm}

Sender

\column{0.95\linewidth}

\includegraphics{../Simulations/nIntGroupNormQual_/evolDyn7_nIntGroup2000.png}

@@

```{r,echo=FALSE,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter01_.png")

@@

```{r,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter11_.png")

@@

<!-- ## Why would you want to be recognized? -->

<!-- ### The peaceful, the aggressive and the clever -->

<!-- ```{r,out.width='90%',fig.show='hold'} -->
<!-- knitr::include_graphics("../Simulations/initAct_/indVarScatter2_.png") -->

<!-- ``` -->

### 2022-08-08 Presentations/ISBE2022.tex
FInal version of the ISBE2022 slides

\begin{frame}{Acknowledgements}
\protect\hypertarget{acknowledgements}{}
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
\includegraphics[width=0.4\textwidth,height=\textheight]{../Images/redouan.jpg}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\includegraphics[width=0.55\textwidth,height=\textheight]{../Images/danielcadena.jpg}
\end{minipage} \\
\midrule
\endhead
\emph{R. Bshary} & \emph{D. Cadena} \\
\includegraphics[width=0.3\textwidth,height=\textheight]{../Images/UNINE_cmjn.jpg}
&
\includegraphics[width=0.3\textwidth,height=\textheight]{../Images/logo_largo.png} \\
\bottomrule
\end{longtable}
\end{frame}

@@

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals}{}
\begin{block}{The handicap principle}
\protect\hypertarget{the-handicap-principle}{}
\begin{center}\includegraphics[height=0.35\textheight]{../Images/Amotz_Zahavi_profile} \includegraphics[height=0.35\textheight]{../Images/sexualSelection} \includegraphics[height=0.35\textheight]{../Images/Grafen} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{ISBE2022_files/figure-beamer/unnamed-chunk-4-1} \end{center}
\vspace{-0.3cm}

@@

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_0} \end{center}
\end{frame}

@@

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_1} \end{center}
\end{frame}

@@

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_2} \end{center}
\end{frame}

@@

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_3} \end{center}
\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-4}{}
\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_5} \end{center}
\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-5}{}
\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_6} \end{center}
\end{frame}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-17-1} \end{center}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-18-1} \end{center}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-19-1} \end{center}

@@

\begin{frame}{Learning mediates the evolution of badges of status
(handicaps)}
\protect\hypertarget{learning-mediates-the-evolution-of-badges-of-status-handicaps}{}
\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/betCostEvol2_/evolDyn18_betCost5} \end{center}
\end{frame}

\begin{frame}{Learning can mediate the evolution of Badges of Status}
\protect\hypertarget{learning-can-mediate-the-evolution-of-badges-of-status}{}
\begin{block}{Individual replicates: no badges}
\protect\hypertarget{individual-replicates-no-badges}{}
\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/betCostEvol2_/evolDyn19_betCost5} \end{center}
\end{block}
\end{frame}

\begin{frame}{The evolution of cheap badges of Status}
\protect\hypertarget{the-evolution-of-cheap-badges-of-status}{}
\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupNormQual_/evolDyn7_nIntGroup2000} \end{center}
\end{frame}

@@

\includegraphics[width=0.45\linewidth]{../Simulations/alphaAct_/alphaAct0.4learnDyn}
\includegraphics[width=0.45\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-24-2}
\end{block}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-1}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-1}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter0_}
\end{block}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-2}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-2}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter1_}
\end{block}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-3}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-3}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter2_}
\end{block}
\end{frame}

>>>>

\begin{frame}{Acknowledgements}
\protect\hypertarget{acknowledgements}{}
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\centering
\includegraphics[width=0.4\textwidth,height=\textheight]{../Images/redouan.jpg}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\includegraphics[width=0.55\textwidth,height=\textheight]{../Images/danielcadena.jpg}
\end{minipage} \\
\midrule()
\endhead
\emph{R. Bshary} & \emph{D. Cadena} \\
\includegraphics[width=0.3\textwidth,height=\textheight]{../Images/UNINE_cmjn.jpg}
&
\includegraphics[width=0.3\textwidth,height=\textheight]{../Images/logo_largo.png} \\
\bottomrule()
\end{longtable}
\end{frame}

@@

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals}{}
\begin{block}{The handicap principle}
\protect\hypertarget{the-handicap-principle}{}
\begin{center}\includegraphics[height=0.45\textheight]{../Images/Amotz_Zahavi_profile} \includegraphics[height=0.45\textheight]{../Images/sexualSelection} \includegraphics[height=0.45\textheight]{../Images/Grafen} \end{center}

\vspace{0.6cm}

@@

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_0} \end{center}
\end{frame}

@@

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_1} \end{center}
\end{frame}

@@

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_3} \end{center}
\end{frame}

@@

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_6} \end{center}
\end{frame}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-12-1} \end{center}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-13-1} \end{center}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-14-1} \end{center}

@@

\begin{frame}{Learning mediates the evolution of badges of status
(handicaps)}
\protect\hypertarget{learning-mediates-the-evolution-of-badges-of-status-handicaps}{}
\begin{columns}[T]

\column{0.05\linewidth}

\tiny
\vspace{1cm}

Receiver

\vspace{2cm}

Evolutionary  \\
Dynamics

\vspace{2cm}

Sender

\column{0.95\linewidth}

\includegraphics{../Simulations/betCostEvol2_/evolDyn18_betCost5_1.png}

\end{columns}
\end{frame}

\begin{frame}{Learning mediates the evolution of badges of status
(handicaps)}
\protect\hypertarget{learning-mediates-the-evolution-of-badges-of-status-handicaps-1}{}
\begin{columns}[T]

\column{0.05\linewidth}

\tiny
\vspace{1cm}

Receiver

\vspace{2cm}

Evolutionary  \\
Dynamics

\vspace{2cm}

Sender

\column{0.95\linewidth}

\includegraphics{../Simulations/betCostEvol2_/evolDyn18_betCost5.png}

\end{columns}
\end{frame}

\begin{frame}{The evolution of cheap badges of Status}
\protect\hypertarget{the-evolution-of-cheap-badges-of-status}{}
\begin{columns}[T]

\column{0.05\linewidth}

\tiny
\vspace{1cm}

Receiver

\vspace{2cm}

Evolutionary  \\
Dynamics

\vspace{2cm}

Sender

\column{0.95\linewidth}

\includegraphics{../Simulations/nIntGroupNormQual_/evolDyn7_nIntGroup2000.png}

\end{columns}
\end{frame}

@@

\includegraphics[width=0.45\linewidth]{../Simulations/alphaAct_/alphaAct0.4learnDyn}
\includegraphics[width=0.45\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-16-2}
\end{block}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-1}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-1}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter01_}
\end{block}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-2}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-2}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter11_}
\end{block}
\end{frame}
